Quantifying uncertainty in Pareto estimates of global lake area

### 2023-02-06 manuscript/manuscript.tex
add paper doi

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.XXX/XXX}}
\renewcommand{\undertitle}{This is an Accepted Manuscript of an article published in Limnology \& Oceanography: Methods \href{https://doi.org/}{DOI: 10.XXX/XXX}}
\renewcommand{\shorttitle}{Pareto lake area uncertainty}

>>>>

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.1002/LOM3.10536}}
\renewcommand{\undertitle}{This is an Accepted Manuscript of an article published in Limnology \& Oceanography: Methods \href{https://doi.org/10.1002/LOM3.10536}{DOI: 10.1002/LOM3.10536}}
\renewcommand{\shorttitle}{Pareto lake area uncertainty}
